Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-28 Geometric types.tex
Adding some todo notes and removing section 4.5

Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$. 
As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
\[
\begin{tikzcd}[column sep = 30]
a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}}\\
m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}{\mu \otimes \id} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u}
\end{tikzcd}
\]
Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local systems on $G$, the converse is certainly not true.

For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in Deligne's category $D^b_c(G;\EE)$.
Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
We see an example of this in Section~\ref{ssec:SL23}.

@@

\subsection{The True Commutator}

Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a linear character sheaf
on $G = \PGL_n$ that does not vanish on $G\der = \PGL_n$, defined by the extension
\[
1 \to \mu_n \to \SL_n \to \PGL_n \to 1
\]
together with a non-trivial character of $\mu_n(k)$. 
In order to obtain a relationship between linear character sheaves on $G$ and characters of $G(k)$,
he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
 Since we have already seen the need to adapt the
notion of character sheaf, even in the commutative case, we instead add restrictions
to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$.

>>>>

Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$. 
As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$. \todo{problem with bottom left of diagram}
\[
\begin{tikzcd}[column sep = 30]
a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}}\\
m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}{\mu \otimes \id} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u}
\end{tikzcd}
\]
Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local system on $G$, the converse is certainly not true.

For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in Deligne's category $D^b_c(G;\EE)$.
Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear \todo{should this be $\EE$-linear?} combination of characteristic functions of Weil character sheaves on $G$.
We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
We will see an example of this in Section~\ref{ssec:SL23}.

@@
